Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-27 awipev-CO2.Rmd
clean-up calculation pH seafet

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ****** $SA$
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019

@@

# $SA$ below
#periode 1, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

# Periode 2, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
#       datetime <= as.POSIXct("2017-09-28 18:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
#       datetime <= as.POSIXct("2017-09-28 18:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# period 03, mean of 4 previous hours for volt int + volt ext
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
#       datetime <= as.POSIXct("2019-09-13 07:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)

# Ce qui suit (7 lignes) est très bizarre
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# ???????? mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
#       datetime <= as.POSIXct("2019-09-13 07:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
#       datetime <= as.POSIXct("2019-09-13 12:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

@@

#### plot
# $SA$ 3 points?
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

@@

[All UWO-Ferrybox data / NearRealTime (NRT) AWI database](https://dashboard.awi.de/data-xxl/overview.jsp)

@@

[Missing data to add to the NRT database](https://docs.google.com/spreadsheets/d/1Cbc4hWyclnBsNsOH_3QDA3AGZfwF4I1HuadfBe1BVjI/edit?usp=sharing)

>>>>

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
##   *****Attention, but no longer used in the script, so no problem

@@

# For this spec pH, some volt int and T seaF data are missing so we use the closest data
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

# For this spec pH, some volt int and T seaF data are missing so we use the closest data
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# For this spec pH, some volt int and T seaF data are missing so we use the closest data
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))

# For this spec pH, some volt int and T seaF data are missing so we use the closest data
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

@@

#### plot
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

@@

@@
